---
title: "Build Advanced R"
author: "Ian Weykamp"
date: "9/9/2020"
output: html_document
---
##
##HW 2
##

```{r,eval=FALSE}
devtools::install_github("hadley/sloop")
devtools::install_github("hadley/emo")

```

install.packages("bookdown")

```{r render, eval = FALSE}
bookdown::render_book("index.Rmd", output_format = "bookdown::pdf_book")
````

The first error encountered: 
##Quitting from lines 4-5 (Introduction.Rmd) 
##Error in dev.control(displaylist = if (record) "enable" else "inhibit") : ##dev.control() called without an open graphics device

Resolved by installing XQuartz and restarting Mac

Second error
##Quitting from lines 80-81 (Names-values.Rmd) 
##Error in library(lobstr) : there is no package called 'lobstr'
##Calls: local ... withCallingHandlers -> withVisible -> eval -> eval -> ##library

install.packages("lobstr")

Third error
##Quitting from lines 535-550 (R6.Rmd) 
##Error in loadNamespace(name) : there is no package called 'RSQLite'
##Calls: local ... loadNamespace -> withRestarts -> withOneRestart -> ##doWithOneRestart

install.packages("RSQLite")

Fourth error
##Quitting from lines 38-40 (Perf-measure.Rmd) 
##Error in library(profvis) : there is no package called 'profvis'
##Calls: local ... withCallingHandlers -> withVisible -> eval -> eval -> ##library

install.packages("profvis")

Fifth error
##uitting from lines 38-40 (Perf-measure.Rmd) 
##Error in library(bench) : there is no package called 'bench'
##Calls: local ... withCallingHandlers -> withVisible -> eval -> eval -> ##library

install.packages("bench")

Sixth error
##Quitting from lines 233-234 (Perf-measure.Rmd) 
##Error: `ggbeeswarm` must be installed to use `type = "beeswarm"` option.

install.packages("ggbeeswarm")

Seventh error
##xcrun: error: invalid active developer path ##(/Library/Developer/CommandLineTools), missing xcrun at: ##/Library/Developer/CommandLineTools/usr/bin/xcrun
##Error in sourceCpp(code = code, env = env, rebuild = rebuild, cacheDir = ##cacheDir,  : 
##  Error 1 occurred building shared library.
##Calls: local ... withVisible -> eval -> eval -> cppFunction -> sourceCpp

Installed xcode for Mac to resolve

Eigth error
##Package fontspec Error: The font "Inconsolata" cannot be found.

Downloaded font Inconsolta from the web and restarted RStudio to resolve
Took two tries because I forgot to install the font.

Nineth Error
##! LaTeX Error: Environment sidebar undefined.
##
##Error: LaTeX failed to compile _main.tex. See ##https://yihui.org/tinytex/r/#debugging for debugging tips. See _main.log ##for more info.

reinstall.packages("tinytex")
remotes::install_github('rstudio/rmarkdown')

